Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling

### 2020-01-24 Ben_Manuscripts/stochastic_transport/Final_Draft.tex
Responded to comments.

%BJC8: from author guidelines. Should there only be a line between column headings?
%Use a single horizontal rule to separate the column headings from the entries in the table. Use horizontal space within the body of the table to separate broad groups of entries. Extra vertical space may be used between columns. Avoid vertical rules in tables. Use lower-case roman letters for footnotes placed at the bottom of a table.

  \begin{table}[!htb]
	  \centering
	  \begin{tabular}{ccc}
	  %\hline
	  Dwell Distribution                & ~~~~~~~~~Hop Length Distribution~~~~~~~~~~~ & Abbreviation \\
	  \hline
      Power Law                         & Gaussian                & sFBM         \\
      Power Law w/ Exponential Cut-off  & Gaussian                & sFBMcut      \\
      Power Law                         & L\'evy Stable           & sFLM         \\
      Power Law w/ Exponential Cut-off  & L\'evy Stable           & sFLMcut      \\
	  %\hline
	  \end{tabular}
	  \caption{We tested four anomalous diffusion models with various modifications 
	  to the dwell and hop length distributions. We incorporate correlation structure
	  into all models.}\label{table:anomalous_models}
 \end{table}

@@

  %BJC3: not sure how to cite fbm
  We used the Python package \texttt{fbm} to generate exact simulations of FBM and our
  own Python implementation of the algorithm by Stoev and Taqqu to simulate FLM.
  \cite{stoev_simulation_2004} Note that, to our knowledge, there are no known exact
  simulation algorithms for generating FLM trajectories. However, the algorithm
  we used sufficiently approximates draws from the marginal distribution and 
  reasonably approximates the correlation structure on MD simulation timescales. We
  added an empirical correction to enhance the accuracy of the correlation structure
  (see Section~\ref{S-section:flm_correlation} of the Supplemental Material for 
  validation of the approach).

@@

  %BJC8: reformatted. I think this is what they want in terms of format
  \begin{table}[!htb]
	  \centering
	  \begin{tabular}{ll}
	  \multicolumn{2}{c}{Markov State-Dependent Dynamical Model State Definitions} \\
	  \hline
	  1. In tails, not trapped                      & 5. In pores, not trapped                     \\
	  2. In tails and hydrogen bonding              & 6. In pores and hydrogen bonding             \\
	  3. In tails and associated with sodium        & 7. In pores and associated with sodium       \\
	  4. In tails, hydrogen bonding and associated  ~~~~& 8. In pores, hydrogen bonding and associated \\
	  %\hline
	  \end{tabular}
	  \caption{We defined 8 discrete states based on all combinations of previously observed solute
	  trapping mechanisms.}\label{table:states}  
  \end{table}

@@

  The one and two mode AD models do a fairly good job of predicting the magnitude of 
  the MD MSD curves examined up to a 1000 ns time lag.
  % when we use truncated power
  %laws to describe the dwell time distributions.
  %MRS8: maybe be a bit more explicit about which choices described above are used here. i.e. did you actually use a Gaussian  distribution because Levy was so close?
  %BJC8: I thought that sFBMcut and sFLMcut implied which distributions I used. It's in Table I
  In most cases, the sFBMcut and sFLMcut models give very similar results, most 
  likely because their $\alpha_h$ parameter values are relatively close to 2, meaning
  the hop length distributions are nearly Gaussian even when fit to a more general 
  L\'evy distribution.

@@

  %MRS8: in section below, it would be useful to add a sentence that answers the ``so, what'' after the structural
  %detail for each molecule - just adds reader interest.
  %BJC8: I'm interpreting this as, "how does this information relate to design"
  Urea spends the largest fraction of its time trapped via association with sodium ions.
  It does so 31\% of the total time while in the tails (state 3) and 21\% of the
  total time while in the pores (state 7). Note that sodium does not drift significantly 
  into the tails but sits close to the pore/tail region boundary. The electron-dense 
  and unshielded oxygen atom of urea's carbonyl group is prone to associate with 
  positively charged sodium ions. The nitrogen atoms of urea are only weak hydrogen bond
  donors. 
  %BJC8: something like this I think.   
  Therefore the transport rate of urea may be enhanced the most by removing or changing 
  the counter-ion identity.
  %MRS8: above seems incomplete - are weak h-bond donors so what?

  Ethylene glycol spends the largest fraction of its time trapped in a hydrogen
  bonded state. It does so 24\% of the total time while in the tails (state 2)
  and 32\% of the total time while in the pores (state 6). The two hydroxyl groups 
  of ethylene glycol readily donate their hydrogen atoms to the carboxylate
  head groups and the ether linkages between the head groups and monomer tails.
  %BJC8: added following sentence
  The transport rate of ethylene glycol might be increased by removing hydrogen 
  bond accepting groups from the LLC monomers, especially those which stabilize
  the solute in the tails (i.e. the ether linkages).

  Methanol spends most of its time unbound in the tail region (state 1) and spends a 
  significant portion of time hydrogen bonded while in the tail region.
  Tail region hydrogen bonds are donated from methanol to the ether linkages between
  the monomer head groups and tails. 
  %BJC8: added  
  If one desires an increased methanol transport 
  rate, the LLC system may benefit most by preventing its partition into the monomer
  tails. This might be achieved by adding cross-linkable groups near the monomer
  head groups.

  Finally, acetic acid spends the majority of its time hydrogen bonding both in and out
  of the pore (states 2 and 6). Although it has an unshielded carbonyl group in its
  structure, association with sodium ions in this environment is apparently a much 
  weaker interaction than hydrogen bonding. 
  %BJC8:added  
  As with ethylene glycol, one might increase
  the transport rate of acetic acid by removing hydrogen bond accepting constituents
  of the LLC monomer. With this modification, we hypothesize that acetic acid would 
  show similar transport rates to urea given their structural similarity.

@@

  %MRS8: IMPORTANT POINT!
  %MRS8: I would play up that there is absolutely no way one could figure this out 
  %MRS8: from looking at the molecules, or the pores, or even the MD trajectories alone.
  %MRS8: There's a lot of complex interplay here that has the potentially to really lead to interesting 
  %MRS8: separations. Even if the models aren't quite right, they show how such selectivtiy CAN arise.
  %BJC8: added a new paragraph after this one.

>>>>

%BJC8: from author guidelines. Should there only be a line between column headings?
%Use a single horizontal rule to separate the column headings from the entries in the table. Use horizontal space within the body of the table to separate broad groups of entries. Extra vertical space may be used between columns. Avoid vertical rules in tables. Use lower-case roman letters for footnotes placed at the bottom of a table.
%MRS9: I'd go with what they said.  Looking at PRE, it looks like you can put double lines above and below the table, though - I added them 
  \begin{table}[!htb]
	  \centering
	  \begin{tabular}{ccc}
            \hline
	  \hline
	  Dwell Distribution                & ~~~~~~~~~Hop Length Distribution~~~~~~~~~~~ & Abbreviation \\
	  \hline
      Power Law                         & Gaussian                & sFBM         \\
      Power Law w/ Exponential Cut-off  & Gaussian                & sFBMcut      \\
      Power Law                         & L\'evy Stable           & sFLM         \\
      Power Law w/ Exponential Cut-off  & L\'evy Stable           & sFLMcut      \\
	  \hline
          \hline
	  \end{tabular}
	  \caption{We tested four anomalous diffusion models with various modifications 
	  to the dwell and hop length distributions. We incorporate correlation structure
	  into all models.}\label{table:anomalous_models}

 \end{table}

@@

  %BJC3: not sure how to cite fbm
  %MRS9: cite github page?
  We used the Python package \texttt{fbm} to generate exact simulations of FBM and our
  own Python implementation of the algorithm by Stoev and Taqqu to simulate FLM.
  \cite{stoev_simulation_2004} Note that, to our knowledge, there are no known exact
  simulation algorithms for generating FLM trajectories. However, the algorithm
  we used sufficiently approximates draws from the marginal distribution and 
  reasonably approximates the correlation structure on MD simulation timescales. We
  added an empirical correction to enhance the accuracy of the correlation structure
  (see Section~\ref{S-section:flm_correlation} of the Supplemental Material for 
  validation of the approach).

@@

  %BJC8: reformatted. I think this is what they want in terms of format
  %MRS9: tweaked 
  \begin{table}[!htb]
	  \centering
	  \begin{tabular}{ll}
            \hline
            \hline
	  \multicolumn{2}{c}{Markov State-Dependent Dynamical Model State Definitions} \\
	  \hline
	  1. In tails, not trapped                      & 5. In pores, not trapped                     \\
	  2. In tails and hydrogen bonding              & 6. In pores and hydrogen bonding             \\
	  3. In tails and associated with sodium        & 7. In pores and associated with sodium       \\
	  4. In tails, hydrogen bonding and associated  ~~~~& 8. In pores, hydrogen bonding and associated \\
	  \hline
          \hline
	  \end{tabular}
	  \caption{We defined 8 discrete states based on all combinations of previously observed solute
	  trapping mechanisms.}\label{table:states}  
  \end{table}

@@

  The one and two mode AD models do a fairly good job of predicting the magnitude of 
  the MD MSD curves examined up to a 1000 ns time lag.
  % when we use truncated power
  %laws to describe the dwell time distributions.
  %MRS8: maybe be a bit more explicit about which choices described above are used here. i.e. did you actually use a Gaussian  distribution because Levy was so close?
  %BJC8: I thought that sFBMcut and sFLMcut implied which distributions I used. It's in Table I
  %MRS9: Maybe say ``both the Brownian (sFBMcut) and Levy (sFBMcut) version of both the one and two AD models''.  I think with the number of models floating around, it helps to be super explicit about what is being considered at any point.
  In most cases, the sFBMcut and sFLMcut models give very similar results, most 
  likely because their $\alpha_h$ parameter values are relatively close to 2, meaning
  the hop length distributions are nearly Gaussian even when fit to a more general 
  L\'evy distribution.

@@

  %MRS8: in section below, it would be useful to add a sentence that answers the ``so, what'' after the structural
  %detail for each molecule - just adds reader interest.
  %BJC8: I'm interpreting this as, "how does this information relate to design" 
  %MRS9: yes.
  Urea spends the largest fraction of its time trapped via association with sodium ions.
  It does so 31\% of the total time while in the tails (state 3) and 21\% of the
  total time while in the pores (state 7). Note that sodium does not drift significantly 
  into the tails but sits close to the pore/tail region boundary. The electron-dense 
  and unshielded oxygen atom of urea's carbonyl group is prone to associate with 
  positively charged sodium ions. The nitrogen atoms of urea are only weak hydrogen bond
  donors. 
  %BJC8: something like this I think.   
  Therefore the transport rate of urea 
  %MRS9 tweak.
  %may be enhanced the most
  is likely to be most significantly modified
  by removing or changing 
  the counter-ion identity.

  Ethylene glycol spends the largest fraction of its time trapped in a hydrogen
  bonded state. It does so 24\% of the total time while in the tails (state 2)
  and 32\% of the total time while in the pores (state 6). The two hydroxyl groups 
  of ethylene glycol readily donate their hydrogen atoms to the carboxylate
  head groups and the ether linkages between the head groups and monomer tails.
  %BJC8: added following sentence
  %MRS9: as above, maybe ``modified'' is the best rather than enhanced?  Maybe we want to slow it down as well. 
  The transport rate of ethylene glycol might be increased by removing hydrogen 
  bond accepting groups from the LLC monomers, especially those which stabilize
  the solute in the tails (i.e. the ether linkages).

  Methanol spends most of its time unbound in the tail region (state 1) and spends a 
  significant portion of time hydrogen bonded while in the tail region.
  Tail region hydrogen bonds are donated from methanol to the ether linkages between
  the monomer head groups and tails. 
  %BJC8: added  
  %MRS9: see above.
  If one desires an increased methanol transport 
  rate, the LLC system may benefit most by preventing its partition into the monomer
  tails. This might be achieved by adding cross-linkable groups near the monomer
  head groups.

  Finally, acetic acid spends the majority of its time hydrogen bonding both in and out
  of the pore (states 2 and 6). Although it has an unshielded carbonyl group in its
  structure, association with sodium ions in this environment is apparently a much 
  weaker interaction than hydrogen bonding. 
  %BJC8:added  
  %MRS9: see above.
  As with ethylene glycol, one might increase
  the transport rate of acetic acid by removing hydrogen bond accepting constituents
  of the LLC monomer. With this modification, we hypothesize that acetic acid 
  %MRS9: 
  %would 
  might 
  show similar transport rates to urea given their structural similarity.

@@

  %MRS8: IMPORTANT POINT!
  %MRS8: I would play up that there is absolutely no way one could figure this out 
  %MRS8: from looking at the molecules, or the pores, or even the MD trajectories alone.
  %MRS8: There's a lot of complex interplay here that has the potentially to really lead to interesting 
  %MRS8: separations. Even if the models aren't quite right, they show how such selectivtiy CAN arise.
  %BJC8: added a new paragraph after this one.
  %MRS9: looks good.
